---
title: "IRC_arthropod_analysis_2020"
author: "Rachel Kenny"
date: "3/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Load libraries & data
```{r load}

# Load packages
library(tidyverse)
library(readxl)
library(readr)
library(janitor)
library(nlme)
library(broom)
library(here)

# Load raw arthropod data
arth_data_raw <- read_xlsx(here("data", "combined arthropod data.xlsx"))

# Load tidy arthropod data
arth_data <- read_csv(here("data", "IRC_restoration_arthropod_data.csv")) %>% 
  clean_names()

# Filter arthropod data from CSS (coastal sage scrub) habitat
arth_css <- arth_data %>% 
  filter(type == "CSS")

# Filter arthropod data from GL (grassland) habitat
arth_gl <- arth_data %>% 
  filter(type == "GL")

##############################

# Load arthropod data with weedy & intact reference sites
arth_ref <- read_csv(here("data", "IRC_restoration_arthropod_data_reference.csv")) %>% 
  clean_names() %>% 
  filter(year_restoration != "0" & year_restoration != "1" & year_restoration != "3")


# Reference CSS
arth_ref_css <- arth_ref %>% 
  filter(type == "CSS" | type == "weedy" | type == "intact")

# Reference GL
arth_ref_gl <- arth_ref %>% 
  filter(type == "GL" | type == "weedy" | type == "intact")

View(arth_data)

```

```{r}
## Check for normality

hist(arth_data$evenness_functional)
hist(arth_data$richness_taxa)
hist(arth_data$richness_ant)

hist(arth_css$evenness_functional)
hist(arth_css$richness_taxa)
hist(arth_css$richness_ant)

hist(arth_gl$evenness_functional)
hist(arth_gl$richness_taxa)
hist(arth_gl$richness_ant)

```


## Linear mixed-effects model
```{r}

# Method 1

library(lme4)

lme1 = lmer(richness_taxa ~ type + year_restoration + (1|transect), data=arth_data)
lme1
summary(lme1)

lme2 = lmer(richness_ant ~ type + year_restoration + (1|transect), data=arth_data)

lme3 = lmer(evenness_functional ~ type + year_restoration + (1|transect), data=arth_data)

dwplot(lme1)
dwplot(lme2)
dwplot(lme3)


# Method 2

# richness - taxa
lme_rich_taxa <- lme(
  fixed = richness_taxa ~ type + year_restoration, 
  random = ~1|transect, 
  data = arth_data)

summary(lme_rich_taxa)

# richness - ants
lme_rich_ant <- lme(
  fixed = richness_ant ~ type + year_restoration, 
  random = ~1|transect, 
  data = arth_data)

summary(lme_rich_ant)


# evenness - functional
lme_even <- lme(
  fixed = evenness_functional ~ type + year_restoration, 
  random = ~1|transect, 
  data = arth_data)

summary(lme_even)


mean(arth_data$richness_taxa)
mean(arth_data$richness_ant)
mean(arth_data$evenness_functional)

install.packages("MuMIn")

```

## Mixed models w/ rainfall
```{r}

# richness - taxa
lme_rich_taxa_rain <- lme(
  fixed = richness_taxa ~ type + rainfall + year_restoration, 
  random = ~1|transect, 
  data = arth_data)

summary(lme_rich_taxa_rain)

# richness - ants
lme_rich_ant_rain <- lme(
  fixed = richness_ant ~ type + rainfall + year_restoration, 
  random = ~1|transect, 
  data = arth_data)

summary(lme_rich_ant_rain)


# evenness - functional
lme_even_rain <- lme(
  fixed = evenness_functional ~ type + rainfall + year_restoration, 
  random = ~1|transect, 
  data = arth_data)

summary(lme_even_rain)

```



```{r}

transects <- unique(arth_data$transect)

write.csv(transects, "transects.csv")

```


## CSS means
```{r}

mean(arth_css$richness_taxa)
mean(arth_css$richness_ant)
mean(arth_css$evenness_functional)

```


## CSS Linear models
```{r}
#CSS Model 1

# richness - taxa 
lme_rich_taxa_css <- lme(
  fixed = richness_taxa ~  year_restoration, 
  random = ~1|transect, 
  data = arth_css)

summary(lme_rich_taxa_css)


# richness - ants 
lme_rich_ant_css <- lme(
  fixed = richness_ant ~ year_restoration, 
  random = ~1|transect, 
  data = arth_css)

summary(lme_rich_ant_css)


# evenness - functional
lme_even_css <- lme(
  fixed = evenness_functional ~  year_restoration, 
  random = ~1|transect, 
  data = arth_css)

summary(lme_even_css)

```

## CSS Linear models w/ rainfall
```{r}
#CSS Model with rain

# richness - taxa 
lme_rich_taxa_css2 <- lme(
  fixed = richness_taxa ~  year_restoration + rainfall, 
  random = ~1|transect, 
  data = arth_css)

summary(lme_rich_taxa_css2)


# richness - ants 
lme_rich_ant_css2 <- lme(
  fixed = richness_ant ~ year_restoration + rainfall, 
  random = ~1|transect, 
  data = arth_css)

summary(lme_rich_ant_css2)


# evenness - functional
lme_even_css2 <- lme(
  fixed = evenness_functional ~  year_restoration + rainfall, 
  random = ~1|transect, 
  data = arth_css)

summary(lme_even_css2)


```

## GL means
```{r}

mean(arth_gl$richness_taxa)
mean(arth_gl$richness_ant)
mean(arth_gl$evenness_functional)

```


## GL Linear models
```{r}
# GL Model 1

# richness - taxa 
lme_rich_taxa_gl <- lme(
  fixed = richness_taxa ~ year_restoration, 
  random = ~1|transect, 
  data = arth_gl)

summary(lme_rich_taxa_gl)


# richness - ants 
lme_rich_ant_gl <- lme(
  fixed = richness_ant ~ year_restoration, 
  random = ~1|transect, 
  data = arth_gl)

summary(lme_rich_ant_gl)


# evenness - functional 
lme_even_gl <- lme(
  fixed = evenness_functional ~  year_restoration, 
  random = ~1|transect, 
  data = arth_gl)

summary(lme_even_gl)

```


## GL Linear models - rain
```{r}
# GL Model 2

# richness - taxa 
lme_rich_taxa_gl2 <- lme(
  fixed = richness_taxa ~ year_restoration + rainfall, 
  random = ~1|transect, 
  data = arth_gl)

summary(lme_rich_taxa_gl2)


# richness - ants 
lme_rich_ant_gl2 <- lme(
  fixed = richness_ant ~ year_restoration + rainfall, 
  random = ~1|transect, 
  data = arth_gl)

summary(lme_rich_ant_gl2)


# evenness - functional 
lme_even_gl2 <- lme(
  fixed = evenness_functional ~  year_restoration + rainfall, 
  random = ~1|transect, 
  data = arth_gl)

summary(lme_even_gl2)

```


## Anova - taxa richness ~ ref_type
```{r}

# What is the effect of the treatment on the value
model=lm(arth_ref$richness_taxa ~ arth_ref$type)

ANOVA=aov(model)
 
# Tukey test to study each pair of treatment :
TUKEY <- TukeyHSD(x=ANOVA, 'arth_ref$type', conf.level=0.95)
 
# Tuckey test representation :
tky_tr_ref <- plot(TUKEY , las=1 , col="blue")

tky_tr_ref

# bar graph taxa richness ~ type
bar_tr_ref <- ggplot(arth_ref) + 
  geom_bar(aes(x = type, y = richness_taxa, fill=type), stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Taxa richness ~ habitat type") +
  xlab("Habitat type") +
  ylab("Taxa richness") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_discrete(expand=c(0.2,0))+
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))+
  scale_fill_brewer(palette="Paired")

bar_tr_ref

```


## Anova - ant species richness ~ ref_type
```{r}

# What is the effect of the treatment on the value
model=lm(arth_ref$richness_ant ~ arth_ref$type)

ANOVA=aov(model)
 
# Tukey test to study each pair of treatment :
TUKEY <- TukeyHSD(x=ANOVA, 'arth_ref$type', conf.level=0.95)
 
# Tuckey test representation :
tky_tr_ref <- plot(TUKEY , las=1 , col="blue")

plot(TUKEY , las=1 , col="blue")

tky_tr_ref

# bar graph ant species richness ~ type
bar_tr_ref <- ggplot(arth_ref) + 
  geom_bar(aes(x = type, y = richness_ant, fill=type), stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("ant species richness ~ habitat type") +
  xlab("Habitat type") +
  ylab("ant species richness") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_discrete(expand=c(0.2,0))+
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))+
  scale_fill_brewer(palette="Paired")

bar_tr_ref

```


## Anova - functional evenness ~ ref_type
```{r}

# What is the effect of the treatment on the value
model=lm(arth_ref$evenness_functional ~ arth_ref$type)

ANOVA=aov(model)
 
# Tukey test to study each pair of treatment :
TUKEY <- TukeyHSD(x=ANOVA, 'arth_ref$type', conf.level=0.95)
 
# Tuckey test representation :
tky_tr_ref <- plot(TUKEY , las=1 , col="blue")

tky_tr_ref

# bar graph functional evenness ~ type
bar_tr_ref <- ggplot(arth_ref) + 
  geom_bar(aes(x = type, y = evenness_functional, fill=type), stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("functional evenness ~ habitat type") +
  xlab("Habitat type") +
  ylab("functional evenness") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_discrete(expand=c(0.2,0))+
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))+
  scale_fill_brewer(palette="Paired")

bar_tr_ref

```


## Proportional biomass - ref
```{r}

arth_data <- read_csv("IRC_restoration_arthropod_data.csv") %>% 
  clean_names()

arth_ref_2 <- arth_ref %>% 
  select(type, transect, year_restoration, detritivores, herb_chew, herb_suck, parasitoid, pollinator, predator, scavenger) %>% 
  gather("functional_group", "proportional_biomass", 4:10)

View(arth_ref_2)

arth_ref_3 <- arth_ref_2
arth_ref_3$type <- as.factor(arth_ref_3$type)

View(arth_ref_3)

# bar graph proportional biomass ~ type

plot_ref_bio <- ggplot(arth_ref_3) + 
  geom_bar(aes(x = type, y = proportional_biomass, fill = functional_group), position = "fill", stat = "summary") +
  theme_classic() +
  ggtitle("Differences in proportional biomass of arthropods\nby habitat type and reference sites") +
  xlab("Habitat type") +
  ylab("Proportional biomass") +
  scale_y_continuous(expand=c(0,0), breaks = c(.2,.4,.6,.8,1))+
  scale_x_discrete(expand=c(0.2,0))+
  scale_fill_brewer("Functional Group",palette="Set2", labels=c("Detritivore", "Herbivore (chewing)", "Herbivore (sucking)", "Parasitoid", "Pollinator", "Predator", "Scavenger")) +
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))

plot_ref_bio

```




## Plots of richness (taxa and ant) and evenness
```{r}

arth_data$year_restoration <- as.factor(arth_data$year_restoration)

# Richness (taxa) plot
plot_rich <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, richness_taxa), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  scale_y_continuous(expand=c(0,0), breaks=(0:13))+
  theme(axis.title.y = element_text(size = 10))+
  ggtitle("Taxa richness ~ Year of restoration")+
  ylab("Taxa richness")+
  xlab("Year of restoration")

plot_rich


plot_rich_habitat <- ggplot(arth_data, aes(fill=type)) + 
  geom_bar(aes(x = year_restoration, richness_taxa), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  scale_y_continuous(expand=c(0,0), breaks=(0:13))+
  theme(axis.title.y = element_text(size = 10))+
  ggtitle("Taxa richness ~ Year of restoration")+
  ylab("Taxa richness")+
  xlab("Year of restoration")+
  scale_fill_brewer(palette="Paired")

plot_rich_habitat


# Richness (ants) plot
plot_rich_ant <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, richness_ant), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  scale_y_continuous(expand=c(0,0))+
  theme(axis.title.y = element_text(size = 10))+
  ggtitle("Ant species richness ~ Year of restoration")+
  ylab("Ant species richness")+
  xlab("Year of restoration")

plot_rich_ant


plot_ant_habitat <- ggplot(arth_data, aes(fill=type)) + 
  geom_bar(aes(x = year_restoration, richness_ant), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  scale_y_continuous(expand=c(0,0), breaks=(0:13))+
  theme(axis.title.y = element_text(size = 10))+
  ggtitle("Ant species richness ~ Year of restoration")+
  ylab("Ant species richness")+
  xlab("Year of restoration")+
  scale_fill_brewer(palette="Paired")

plot_ant_habitat


# Evenness plot
plot_even <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, evenness_functional), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  scale_y_continuous(expand=c(0,0))+
  theme(axis.title.y = element_text(size = 10))+
  ggtitle("Functional evenness ~ Year of restoration")+
  ylab("Functional evenness")+
  xlab("Year of restoration")

plot_even

plot_even_habitat <- ggplot(arth_data, aes(fill=type)) + 
  geom_bar(aes(x = year_restoration, evenness_functional), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  scale_y_continuous(expand=c(0,0), breaks=(0:13))+
  theme(axis.title.y = element_text(size = 10))+
  ggtitle("Functional evenness ~ Year of restoration")+
  ylab("Functional evenness")+
  xlab("Year of restoration")+
  scale_fill_brewer(palette="Paired")

plot_even_habitat

ggsave("barplot1_rich.png", plot = plot_rich, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)
ggsave("barplot2_rich_habitat.png", plot = plot_rich_habitat, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)
ggsave("barplot3_rich_ant.png", plot = plot_rich_ant, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)
ggsave("barplot4_ant_habitat.png", plot = plot_ant_habitat, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)
ggsave("barplot5_even.png", plot = plot_even, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)
ggsave("barplot6_even_habitat.png", plot = plot_even_habitat, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)

```


## Plots of functional groups
```{r}
arth_data_2 <- arth_data %>% 
  select(transect, year_restoration, detritivores, herb_chew, herb_suck, parasitoid, pollinator, predator, scavenger) %>% 
  gather("functional_group", "proportional_biomass", 3:9)

View(arth_data_2)

arth_data_3 <- arth_data_2
arth_data_3$year_restoration <- as.factor(arth_data_3$year_restoration)

# All
plot_all <- ggplot(arth_data_3) + 
  geom_bar(aes(x = year_restoration, y = proportional_biomass, fill = functional_group), position = "fill", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Changes in proportional biomass of arthropods over time") +
  xlab("Year of restoration") +
  ylab("Proportional biomass") +
  scale_y_continuous(expand=c(0,0), breaks = c(.2,.4,.6,.8,1))+
  scale_x_discrete(expand=c(0.2,0))+
  scale_fill_brewer("Functional Group",palette="Set2", labels=c("Detritivore", "Herbivore (chewing)", "Herbivore (sucking)", "Parasitoid", "Pollinator", "Predator", "Scavenger")) +
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))

plot_all

ggsave("plot_relative_biomass.png", plot = plot_all, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)

```

## Habitat specifc pllots: CSS
```{r}

arth_data_2css <- arth_css %>% 
  select(transect, year_restoration, detritivores, herb_chew, herb_suck, parasitoid, pollinator, predator, scavenger) %>% 
  gather("functional_group", "proportional_biomass", 3:9)

arth_data_3css <- arth_data_2css
arth_data_3css$year_restoration <- as.factor(arth_data_3css$year_restoration)


# All
plot_css <- ggplot(arth_data_3css) + 
  geom_bar(aes(x = year_restoration, y = proportional_biomass, fill = functional_group), position = "fill", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Changes in proportional biomass of arthropods over time") +
  xlab("Year of restoration") +
  ylab("Proportional biomass") +
  scale_y_continuous(expand=c(0,0), breaks = c(.2,.4,.6,.8,1))+
  scale_x_discrete(expand=c(0.2,0))+
  scale_fill_brewer("Functional Group",palette="Set2", labels=c("Detritivore", "Herbivore (chewing)", "Herbivore (sucking)", "Parasitoid", "Pollinator", "Predator", "Scavenger")) +
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))

plot_css

ggsave("plot_relative_biomass_css.png", plot = plot_css, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)

```

## Habitat specifc plots: GL
```{r}

arth_data_2gl <- arth_gl %>% 
  select(transect, year_restoration, detritivores, herb_chew, herb_suck, parasitoid, pollinator, predator, scavenger) %>% 
  gather("functional_group", "proportional_biomass", 3:9)

arth_data_3gl <- arth_data_2gl
arth_data_3gl$year_restoration <- as.factor(arth_data_3gl$year_restoration)


# All
plot_gl <- ggplot(arth_data_3gl) + 
  geom_bar(aes(x = year_restoration, y = proportional_biomass, fill = functional_group), position = "fill", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Changes in proportional biomass of arthropods over time") +
  xlab("Year of restoration") +
  ylab("Proportional biomass") +
  scale_y_continuous(expand=c(0,0), breaks = c(.2,.4,.6,.8,1))+
  scale_x_discrete(expand=c(0.2,0))+
  scale_fill_brewer("Functional Group",palette="Set2", labels=c("Detritivore", "Herbivore (chewing)", "Herbivore (sucking)", "Parasitoid", "Pollinator", "Predator", "Scavenger")) +
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))

plot_gl

ggsave("plot_relative_biomass_gl.png", plot = plot_gl, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)

```

## Proportional biomass: Scatter plot
```{r}

arth_data <- read_csv("IRC_restoration_arthropod_data.csv") %>% 
  clean_names()

arth_data_2 <- arth_data %>% 
  select(transect, year_restoration, detritivores, herb_chew, herb_suck, parasitoid, pollinator, predator, scavenger) %>% 
  gather("functional_group", "proportional_biomass", 3:9)

# lm_eqn <- function(arth_data_2){
#     m <- lm(proportional_biomass ~ year_restoration, arth_data_2);
#     eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
#          list(a = format(unname(coef(m)[1]), digits = 2),
#               b = format(unname(coef(m)[2]), digits = 2),
#              r2 = format(summary(m)$r.squared, digits = 3)))
#     as.character(as.expression(eq));
# }

library(ggpubr)



# plot_scatter <- ggplot(arth_data_2, aes(x = year_restoration, y = proportional_biomass, color = functional_group)) + 
#   geom_point() + 
#   ggtitle("Title") +
#   geom_smooth(method = "lm", fill = NA) +
#   theme_classic() +
#   ggtitle("Changes in proportional biomass of arthropods over time") +
#   xlab("Year of restoration") +
#   ylab("Proportional biomass") +
#   ylim(0,1) +
#   scale_x_continuous(expand=c(0.1,0), breaks =c(0,1,2,3,4,5)) +
#   scale_color_brewer("Functional Group",palette="Set2", labels=c("Detritivore", "Herbivore (chewing)", "Herbivore (sucking)", "Parasitoid", "Pollinator", "Predator", "Scavenger")) +
#   theme(plot.title = element_text(face="bold", size = 11),
#         axis.title = element_text(size=8),
#         legend.title = element_text(size=8, face="bold"),
#         legend.text = element_text(size=8))+ 
#   geom_text(x = 25, y = 300, label = lm_eqn(df), parse = TRUE)

plot_scatter2 <- ggscatter(arth_data_2, x = "year_restoration", y = "proportional_biomass", color = "functional_group", add = "reg.line") + 
  ggtitle("Title") +
  geom_smooth(method = "lm", fill = NA) +
  theme_classic() +
  ggtitle("Changes in proportional biomass of arthropods over time") +
  xlab("Year of restoration") +
  ylab("Proportional biomass") +
  ylim(0,1) +
  scale_x_continuous(expand=c(0.1,0), breaks =c(0,1,2,3,4,5)) +
  scale_color_brewer("Functional Group",palette="Set2", labels=c("Detritivore", "Herbivore (chewing)", "Herbivore (sucking)", "Parasitoid", "Pollinator", "Predator", "Scavenger")) +
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8)) +
  facet_wrap(~functional_group) +
  stat_cor(label.y = .9) +
  stat_regline_equation(label.y = .75) 

plot_scatter2

ggsave("plot_relative_biomass_scatter.png", plot = plot_scatter, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)


```

## Individual linear models prop biomass
```{r}

# All data
lm_det <- lm(detritivores ~ year_restoration, data = arth_data)
summary(lm_det)

lm_hrbc <- lm(herb_chew ~ year_restoration, data = arth_data)
summary(lm_hrbc)

lm_hrbs <- lm(herb_suck ~ year_restoration, data = arth_data)
summary(lm_hrbs)

lm_par <- lm(parasitoid ~ year_restoration, data = arth_data)
summary(lm_par)

lm_pol <- lm(pollinator ~ year_restoration, data = arth_data)
summary(lm_pol)

lm_pred <- lm(predator ~ year_restoration, data = arth_data)
summary(lm_pred)

lm_scv <- lm(scavenger ~ year_restoration, data = arth_data)
summary(lm_scv)

# CSS
lm_det_css <- lm(detritivores ~ year_restoration, data = arth_css)
summary(lm_det_css)

lm_hrbc_css <- lm(herb_chew ~ year_restoration, data = arth_css)
summary(lm_hrbc_css)

lm_hrbs_css <- lm(herb_suck ~ year_restoration, data = arth_css)
summary(lm_hrbs_css)

lm_par_css <- lm(parasitoid ~ year_restoration, data = arth_css)
summary(lm_par_css)

lm_pol_css <- lm(pollinator ~ year_restoration, data = arth_css)
summary(lm_pol_css)

lm_pred_css <- lm(predator ~ year_restoration, data = arth_css)
summary(lm_pred_css)

lm_scv_css <- lm(scavenger ~ year_restoration, data = arth_css)
summary(lm_scv_css)

# GL
lm_det_gl <- lm(detritivores ~ year_restoration, data = arth_gl)
summary(lm_det_gl)

lm_hrbc_gl <- lm(herb_chew ~ year_restoration, data = arth_gl)
summary(lm_hrbc_gl)

lm_hrbs_gl <- lm(herb_suck ~ year_restoration, data = arth_gl)
summary(lm_hrbs_gl)

lm_par_gl <- lm(parasitoid ~ year_restoration, data = arth_gl)
summary(lm_par_gl)

lm_pol_gl <- lm(pollinator ~ year_restoration, data = arth_gl)
summary(lm_pol_gl)

lm_pred_gl <- lm(predator ~ year_restoration, data = arth_gl)
summary(lm_pred_gl)

lm_scv_gl <- lm(scavenger ~ year_restoration, data = arth_gl)
summary(lm_scv_gl)

library(knitr)

tbl <- tidy(lm_scv_gl)
tbl

kable(tbl)


library(stargazer)
stargazer(lm_scv_gl, type = "text")

library(broom)

m1 <- tidy(lm_pol_gl) 
m2 <- tidy(lm_pred_gl)
m3 <- tidy(lm_scv_gl)
# Note that tidy() from the broom package is used to convert each model to a data frame

all_models <- bind_rows(
    m1 %>% mutate(model = 1),
    m2 %>% mutate(model = 2),
    m3 %>% mutate(model = 3),
    )

all_models

ols_table <- all_models %>%
    select(-statistic, -p.value) %>%
    mutate_each(funs(round(., 2)), -term) %>% 
    gather(key, value, estimate:std.error) %>%
    spread(model, value) 

ols_table

lm_det_css <- lm(detritivores ~ year_restoration, data = arth_css)
summary(lm_det_css)

lm_hrbc_css <- lm(herb_chew ~ year_restoration, data = arth_css)
summary(lm_hrbc_css)

lm_hrbs_css <- lm(herb_suck ~ year_restoration, data = arth_css)
summary(lm_hrbs_css)

lm_par_css <- lm(parasitoid ~ year_restoration, data = arth_css)
summary(lm_par_css)

lm_pol_css <- lm(pollinator ~ year_restoration, data = arth_css)
summary(lm_pol_css)

lm_pred_css <- lm(predator ~ year_restoration, data = arth_css)
summary(lm_pred_css)

lm_scv_css <- lm(scavenger ~ year_restoration, data = arth_css)
summary(lm_scv_css)

library(stargazer)

stargazer(lm_det_css, lm_hrbc_css, lm_hrbs_css, title="Results", align=TRUE, type="text")



str(lm_det_css)

```


## Individual linear models prop biomass 2
```{r}

# CSS2
lm_det_css <- lm(detritivores ~ year, data = arth_css)
summary(lm_det_css)

lm_hrbc_css <- lm(herb_chew ~ year, data = arth_css)
summary(lm_hrbc_css)

lm_hrbs_css <- lm(herb_suck ~ year, data = arth_css)
summary(lm_hrbs_css)

lm_par_css <- lm(parasitoid ~ year, data = arth_css)
summary(lm_par_css)

lm_pol_css <- lm(pollinator ~ year, data = arth_css)
summary(lm_pol_css)

lm_pred_css <- lm(predator ~ year, data = arth_css)
summary(lm_pred_css)

lm_scv_css <- lm(scavenger ~ year, data = arth_css)
summary(lm_scv_css)

# GL2
lm_det_gl <- lm(detritivores ~ year, data = arth_gl)
summary(lm_det_gl)

lm_hrbc_gl <- lm(herb_chew ~ year, data = arth_gl)
summary(lm_hrbc_gl)

lm_hrbs_gl <- lm(herb_suck ~ year, data = arth_gl)
summary(lm_hrbs_gl)

lm_par_gl <- lm(parasitoid ~ year, data = arth_gl)
summary(lm_par_gl)

lm_pol_gl <- lm(pollinator ~ year, data = arth_gl)
summary(lm_pol_gl)

lm_pred_gl <- lm(predator ~ year, data = arth_gl)
summary(lm_pred_gl)

lm_scv_gl <- lm(scavenger ~ year, data = arth_gl)
summary(lm_scv_gl)


# CSS3
lm_det_css <- lm(detritivores ~ year + rainfall, data = arth_css)
summary(lm_det_css)

lm_hrbc_css <- lm(herb_chew ~ year + rainfall, data = arth_css)
summary(lm_hrbc_css)

lm_hrbs_css <- lm(herb_suck ~ year + rainfall, data = arth_css)
summary(lm_hrbs_css)

lm_par_css <- lm(parasitoid ~ year + rainfall, data = arth_css)
summary(lm_par_css)

lm_pol_css <- lm(pollinator ~ year + rainfall, data = arth_css)
summary(lm_pol_css)

lm_pred_css <- lm(predator ~ year + rainfall, data = arth_css)
summary(lm_pred_css)

lm_scv_css <- lm(scavenger ~ year + rainfall, data = arth_css)
summary(lm_scv_css)

# GL3
lm_det_gl <- lm(detritivores ~ year + rainfall, data = arth_gl)
summary(lm_det_gl)

lm_hrbc_gl <- lm(herb_chew ~ year + rainfall, data = arth_gl)
summary(lm_hrbc_gl)

lm_hrbs_gl <- lm(herb_suck ~ year + rainfall, data = arth_gl)
summary(lm_hrbs_gl)

lm_par_gl <- lm(parasitoid ~ year + rainfall, data = arth_gl)
summary(lm_par_gl)

lm_pol_gl <- lm(pollinator ~ year + rainfall, data = arth_gl)
summary(lm_pol_gl)

lm_pred_gl <- lm(predator ~ year + rainfall, data = arth_gl)
summary(lm_pred_gl)

lm_scv_gl <- lm(scavenger ~ year + rainfall, data = arth_gl)
summary(lm_scv_gl)


```


## CSS Proportional biomass: Scatter plot
```{r}

# , breaks=seq(0:1, by=.2)

plot_scatter_css <- ggplot(arth_data_2css, aes(x = year_restoration, y = proportional_biomass, color = functional_group)) + 
  geom_point() + 
  ggtitle("Title") +
  geom_smooth(method = "lm", fill = NA) +
  theme_classic() +
  ggtitle("Changes in proportional biomass of arthropods over time") +
  xlab("Year of restoration") +
  ylab("Proportional biomass") +
  ylim(0,1) +
  scale_x_continuous(expand=c(0.1,0), breaks =c(0,1,2,3,4,5)) +
  scale_color_brewer("Functional Group",palette="Set2", labels=c("Detritivore", "Herbivore (chewing)", "Herbivore (sucking)", "Parasitoid", "Pollinator", "Predator", "Scavenger")) +
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))

plot_scatter_css

ggsave("plot_relative_biomass_scatter_css.png", plot = plot_scatter_css, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)

```

Rainfall actual biomass models
```{r}

library(stargazer)

View(arth_css)

library(jtools)
library(huxtable)
library(broom)


# CSS rainfall models
lm_det_css <- lm(vol_detritivores ~ year_restoration + rainfall, data = arth_css)
summary(lm_det_css)
summ(lm_det_css)
export_summs(lm_det_css)


lm_det_css <- lm(vol_detritivores ~ year_restoration + rainfall, data = arth_css)
summary(lm_det_css)
summ(lm_det_css)

lm_hrbc_css <- lm(vol_herb_chew ~ year_restoration + rainfall, data = arth_css)
summary(lm_hrbc_css)
summ(lm_hrbc_css)

lm_hrbs_css <- lm(vol_herb_suck ~ year_restoration + rainfall, data = arth_css)
summary(lm_hrbs_css)
summ(lm_hrbs_css)

lm_par_css <- lm(vol_parasitoid ~ year_restoration + rainfall, data = arth_css)
summary(lm_par_css)
summ(lm_par_css)

lm_pol_css <- lm(vol_pollinator ~ year_restoration + rainfall, data = arth_css)
summary(lm_pol_css)
summ(lm_pol_css)

lm_pred_css <- lm(vol_predator ~ year_restoration + rainfall, data = arth_css)
summary(lm_pred_css)
summ(lm_pred_css)

lm_scv_css <- lm(vol_scavenger ~ year_restoration + rainfall, data = arth_css)
summary(lm_scv_css)
summ(lm_scv_css)

table(lm_det_css)

install.packages("devtools")

devtools::install_github("ewenharrison/finalfit")

library(broom)
library(sjPlot)
library(sjmisc)
library(sjlabelled)

tab_model(lm_det_css)

```

## GL actual biomass models
```{r}
# GL3
lm_det_gl <- lm(vol_detritivores ~ year_restoration + rainfall, data = arth_gl)
summary(lm_det_gl)
summ(lm_det_gl)

lm_hrbc_gl <- lm(vol_herb_chew ~ year_restoration + rainfall, data = arth_gl)
summary(lm_hrbc_gl)
summ(lm_hrbc_gl)

lm_hrbs_gl <- lm(vol_herb_suck ~ year_restoration + rainfall, data = arth_gl)
summary(lm_hrbs_gl)
summ(lm_hrbs_gl)

lm_par_gl <- lm(vol_parasitoid ~ year_restoration + rainfall, data = arth_gl)
summary(lm_par_gl)
summ(lm_par_gl)

lm_pol_gl <- lm(vol_pollinator ~ year_restoration + rainfall, data = arth_gl)
summary(lm_pol_gl)
summ(lm_pol_gl)

lm_pred_gl <- lm(vol_predator ~ year_restoration + rainfall, data = arth_gl)
summary(lm_pred_gl)
summ(lm_pred_gl)

lm_scv_gl <- lm(vol_scavenger ~ year_restoration + rainfall, data = arth_gl)
summary(lm_scv_gl)
summ(lm_scv_gl)

```

```



## GL Proportional biomass: Scatter plot
```{r}

# , breaks=seq(0:1, by=.2)

plot_scatter_gl <- ggplot(arth_data_2gl, aes(x = year_restoration, y = proportional_biomass, color = functional_group)) + 
  geom_point() + 
  ggtitle("Title") +
  geom_smooth(method = "lm", fill = NA) +
  theme_classic() +
  ggtitle("Changes in proportional biomass of arthropods over time") +
  xlab("Year of restoration") +
  ylab("Proportional biomass") +
  ylim(0,1) +
  scale_x_continuous(expand=c(0.1,0), breaks =c(0,1,2,3,4,5)) +
  scale_color_brewer("Functional Group",palette="Set2", labels=c("Detritivore", "Herbivore (chewing)", "Herbivore (sucking)", "Parasitoid", "Pollinator", "Predator", "Scavenger")) +
  theme(plot.title = element_text(face="bold", size = 11),
        axis.title = element_text(size=8),
        legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))

plot_scatter_gl

ggsave("plot_relative_biomass_scatter_gl.png", plot = plot_scatter_gl, device = "png", width = 5, height = 3, units = c("in"), dpi = 300)

```


Proportional biomass: individual bar graphs
```{r}
# Detritivores
plot1 <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, detritivores), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Relative cover of detritivores") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_continuous(breaks = 0:5)+
  theme(axis.title.y = element_text(size = 10))

plot1

# Herbivores (chew)
plot2 <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, herb_chew), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Relative cover of herbivores (chewing)") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_continuous(breaks = 0:5)+
  theme(axis.title.y = element_text(size = 10))

plot2


# Herbivores (chew)
plot3 <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, herb_suck), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Relative cover of herbivores (sucking)") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_continuous(breaks = 0:5)+
  theme(axis.title.y = element_text(size = 10))

plot3


# Parasitoids
plot4 <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, parasitoid), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Relative cover of parasitoids") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_continuous(breaks = 0:5)+
  theme(axis.title.y = element_text(size = 10))

plot4


# Pollinators
plot5 <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, pollinator), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Relative cover of pollinators") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_continuous(breaks = 0:5)+
  theme(axis.title.y = element_text(size = 10))

plot5


# Pollinators
plot6 <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, predator), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Relative cover of predators") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_continuous(breaks = 0:5)+
  theme(axis.title.y = element_text(size = 10))

plot6


# Pollinators
plot7 <- ggplot(arth_data) + 
  geom_bar(fill='deepskyblue3', aes(x = year_restoration, scavenger), 
           position = "dodge", stat = "summary", fun.y = "mean") +
  theme_classic() +
  ggtitle("Relative cover of scavengers") +
  scale_y_continuous(expand=c(0,0))+
  scale_x_continuous(breaks = 0:5)+
  theme(axis.title.y = element_text(size = 10))

plot7

```





